Supplementary Information: Vulnerability of tree growth

### 2025-03-04 doc/manuscript.Rmd
results draft

@@

Crown exposure was associated with stronger negative sensitivities in both droughts.

Accounting for effects of exposure, remaining effects of size on sensitivity was different between the two droughts.

![***Figure 5: Effects of size, exposure and water availability*** For comments - https://github.com/forestgeo/growth-precip-thailand/issues/14](display/Fig5_alternate2.png)

>>>>

```{r exposure models, echo=F, warning=F, message=F}
coefs_spre_cii <- coefs_df_spre %>% filter(param == "bsp_sensprop_mocii_min1")
coefs_spre_ordcii <- coefs_df_spre %>% filter(param == "b_orderedciimin1_calcDBH_min1_scaled")
```

@@

Crown exposure was associated with stronger negative sensitivities in both droughts.
In the same models with species random effects on intercept and slope, the simplex parameter for the ordered factor crown exposure in 2010 was significant and negative (median effect =`r round(coefs_spre_cii$median[coefs_spre_cii$yr==2010],2)`, 90% CI `r round(coefs_spre_cii$lwr[coefs_spre_cii$yr==2010],2)`, `r round(coefs_spre_cii$upr[coefs_spre_cii$yr==2010],2)`), while in 2015 the negative effect was not as strong (median effect =`r round(coefs_spre_cii$median[coefs_spre_cii$yr==2015],2)`, 90% CI `r round(coefs_spre_cii$lwr[coefs_spre_cii$yr==2015],2)`, `r round(coefs_spre_cii$upr[coefs_spre_cii$yr==2015],2)`). 
Predicted effects of crown exposure on sensitivity decreased monotonically, with a decrease to negative sensitivities in category 4 and 5 in 2010, but all crown exposure categories had negative sensitivities in 2015 (Fig 5b).

Accounting for effects of exposure, remaining effects of size on sensitivity differed between the two droughts. 
DBH was a significant predictor of exposure category, with larger DBH associated with higher exposure categories in 2010 (median effect =`r round(coefs_spre_ordcii$median[coefs_spre_ordcii$yr==2010],2)`, 90% CI `r round(coefs_spre_ordcii$lwr[coefs_spre_ordcii$yr==2010],2)`, `r round(coefs_spre_ordcii$upr[coefs_spre_ordcii$yr==2010],2)`) and 2015 (median effect =`r round(coefs_spre_ordcii$median[coefs_spre_ordcii$yr==2015],2)`, 90% CI `r round(coefs_spre_ordcii$lwr[coefs_spre_ordcii$yr==2015],2)`, `r round(coefs_spre_ordcii$upr[coefs_spre_ordcii$yr==2015],2)`) (Fig 5a). 
Controlling for this direct effect of exposure, the effect of exposure, the remaining effect of size *per se* was significantly positive in 2010, while it was weakly negative in 2015 (Fig 4a, Fig 5a).

![***Figure 5: Effects of size, exposure and water availability*** For comments - https://github.com/forestgeo/growth-precip-thailand/issues/14](display/Fig5.png)
